---
title: "Final Assessement Cytomegalivirus"
author: "Meret Pfister"
date: "`r date()`"
format:
  html:
    toc: true
    code-fold: show
    code-tools: true
    df-print: paged
    embed-resources: true
  pdf:
    toc: true
  docx:
    toc: true
---

```{r}
#| output: false
# Load libraries
library(here)
library(tidyverse)
library(medicaldata)
library(lubridate)
```

## Introduction

The aim of this report is to visualize de amount of Patients per diagnosis who underwent T-cell replete, matched sibling donor reduced-intensity conditioning allogeneic hematopoietic stem cell transplant. The 13 different diagnosis are Non-Hodgknin- and Hodgkin-Lymphomas, such as anemias and renal carcinoma.

## Data

We read and process the data of laboratory-confirmed Cytomegalyvirus

```{r}
#| output: false
# Read data
data <- cytomegalovirus
```

```{r}
# Process data
data_f <- data |>
  mutate(diagnosis = factor(diagnosis))
```


```{r}
data_counts <- data %>%
  group_by(diagnosis) %>%
  count()
```
## Visualization
```{r}
ggplot(data_counts, aes(x= diagnosis, y = n)) + geom_bar(stat="identity") + theme (axis.text.x = element_text(angle = 45, hjust = 1))
```



## Conclusions

The number of Cytomegalyvirus cases can be differ by diagnosis. In this study, there were 64 cases and 13 different diagnosis.
