---
title: "Final Assessement Cytomegalivirus"
author: "Meret Pfister"
date: "`r date()`"
format:
  html:
    toc: true
    code-fold: show
    code-tools: true
    df-print: paged
    embed-resources: true
  pdf:
    toc: true
  docx:
    toc: true
---

```{r}
#| output: false
# Load libraries
library(here)
library(tidyverse)
library(medicaldata)
library(lubridate)
```

## Introduction

The aim of this exercise is to visualize the increase in laboratory-confirmed cases of COVID-19 in Switzerland during autumn 2020.

## Data

We read and process the data of laboratory-confirmed cases of COVID-19 in Switzerland as reported by the [Federal Office of Public Health](https://idd.bag.admin.ch/).

```{r}
#| output: false
# Read data
data <- cytomegalovirus
```

```{r}
# Process data
data_f <- data |>
  mutate(diagnosis = factor(diagnosis))
```


```{r}
data_counts <- data %>%
  group_by(diagnosis) %>%
  count()
```
## Visualization
```{r}
ggplot(data_counts, aes(x= diagnosis, y = n)) + geom_bar(stat="identity") + theme (axis.text.x = element_text(angle = 45, hjust = 1))
```



## Conclusions

The number of laboratory-confirmed cases of COVID-19 in Switzerland rapidly increased during October 2020 and subsequently declined.
